---
title: "Reproducible Research: Peer Assessment 2"
output: html_document
keep_md: true
---
#Impact of Severe Weather Events on Public Health and Economy in the United States

## Synopsis
In this report, we aim to analyze the impact of different weather events on public health and economy based on the storm database collected from the U.S. National Oceanic and Atmospheric Administration's (NOAA) from 1950 - 2011. We will use the estimates of fatalities, injuries, property and crop damage to decide which types of event are most harmful to the population health and economy. From these data, we found that excessive heat and tornado are most harmful with respect to population health, while flood, drought, and hurricane/typhoon have the greatest economic consequences.

## Data Processing
Libraries used in this analysis
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library("reshape2")
library(R.utils)
```
Download the data file and unzip it.
```{r}
if(!file.exists("./StormData.csv")){
fileUrl <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2FStormData.csv.bz2"
download.file(fileUrl, destfile="./StormData.csv.bz2", method="curl")
bunzip2("./stormData.csv.bz2", overwrite=T, remove=F)
}
```
Then, we read the generated csv file.
```{r}
data <- read.csv(bzfile("./StormData.csv"), header = TRUE, sep=",")
head(data)
```

#Results
##Question 1: Across the United States, which types of events (as indicated in the ð™´ðš…ðšƒðšˆð™¿ð™´ variable) are most harmful with respect to population health?
```{r}
data$totalharm <- data$FATALITIES + data$INJURIES
mostharm <- data$EVTYPE[which(data$totalharm == max(data$totalharm))]
mostharm
```

##Question 2: Across the United States, which types of events have the greatest economic consequences?